E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-14 Discussion/mitigation.tex
HUGE changes

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
	\begin{table}[!htbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website: https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

>>>>

	Using libraries such as PEAR Mail, PHPMailer, Apache Commons E-Mail, Contact Form 7, and Swiftmailer can significantly reduce the occurrence of E-Mail Header Injection vulnerability.
	\begin{table}[!htbp]
		\centering
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\tablefootnote{PEAR Mail Website: https://pear.php.net/package/Mail}, PHPMailer\tablefootnote{PHPMailer Website:\\ https://github.com/PHPMailer/PHPMailer}, Swiftmailer\tablefootnote{Swiftmailer Website: http://swiftmailer.org/}}}\\
			\hline
			Python & SMTPLib with email.header.Header\tablefootnote{instead of using email.parser.Parser to parse the header}\\
			\hline
			Java & Apache Commons E-Mail\tablefootnote{Apache Commons E-Mail: https://commons.apache.org/proper/commons-email/}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\tablefootnote{Ruby Mail Website: https://rubygems.org/gems/mail}\\
			\hline
			WordPress & Contact Form 7\tablefootnote{Contact Form 7 Download: https://wordpress.org/plugins/contact-form-7/}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}
	\item Use a Content Management System (CMS) \\
	Content management systems like WordPress and Drupal include certain libraries and plugins to prevent E-Mail Header Injection. Thus, websites built with such CMS' are usually resistant to these attacks. However, it is advised to use the right E-Mail plugins when using such CMS', as not all plugins might be secure.
	An example of a secure plug-in is included as part of Table~\ref{tab:maillib}.

### 2016-05-14 Results/analysis.tex
HUGE changes

\subsection[Analysis of Data]{Our Analysis of the received e-mail Data}
During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
\begin{enumerate}
	\item E-Mails with the \texttt{bcc} header successfully injected\\
	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails. This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.

>>>>

\subsection{Analysis of the received e-mail data}
During our analysis of the received e-mails, we found that the e-mails that we received belonged to one of three broad categories:
\begin{enumerate}
	\item E-Mails with the \texttt{bcc} header successfully injected\\
	This form of injection was our initial objective and we found 265 such e-mails in our received e-mails. This indicates that the websites that sent out these e-mails are vulnerable to e-mail header injection, where we could inject and manipulate any header.

### 2016-05-14 Results/data_analysis.tex
HUGE changes

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{S.No}} &
		\multicolumn{1}{c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		1 & E-Mail Header Injections with `bcc' header & 265\\
		\hline
		2 & E-Mail Header Injections with `x-check' header & 214\\
		\hline
		3 & `To header' injections alone & 142\\
		\hline
		4 & E-Mail Header Injections with `bcc' and `x-check' headers & 188\\
		\hline
		5 & Both `To header' injections and x-check headers &
		11\\
		\hline
		6 & `x-check' headers found in `nuser' e-mails & 56\\
		\hline
		7 & Unique `x-check' headers found in `nuser' e-mails & 26\\
		\hline
		8 & Total successful injections (1 + 3 + 7) & 433\\

		\hline
	\end{tabular}
	\caption[\titlecap{Analysis of the data}]{Classification of the e-mails that we received into broad categories of the vulnerability.}
	\label{tab:analysis}
\end{table}

>>>>

\begin{table*}[!htbp]
	\centering
	\begin{tabular}{|l|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Type of Injection}} &
		\multicolumn{1}{p{3cm}|}{\centering \textbf{No. of e-mails received}}\\
		\hline
		E-Mail Header Injections with \texttt{bcc} header & 304\\
		\hline
		E-Mail Header Injections with \texttt{x-check} header & 252\\
		\hline
		\texttt{To header} injections alone & 157\\
		\hline
		E-Mail Header Injections with \texttt{bcc} and \texttt{x-check} headers & 216\\
		\hline
		Both \texttt{To header} injections and x-check headers &
		12\\
		\hline
		\texttt{x-check} headers found in \texttt{nuser} e-mails & 67\\
		\hline
		Unique \texttt{x-check} headers found in \texttt{nuser} e-mails & 35\\
		\hline
		Total successful injections (1 + 3 + 7) & 496\\

		\hline
	\end{tabular}
	\caption[\titlecap{Analysis of the data}]{Classification of the e-mails that we received into broad categories of the vulnerability.}
	\label{tab:analysis}
\end{table*}

### 2016-05-14 Results/pipeline.tex
chap5 added
HUGE changes

\section[The Pipeline]{Understanding the pipeline}
This section serves to represent our pipeline quantitatively and graphically. Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

@@

\begin{figure}
	\centering
	\includegraphics[width=16cm, height=9cm]{Results/emailheaderpipeline}
	\caption[\titlecap{E-Mail header injection Pipeline}]{Pipeline - shows the quantity of data gathered at each stage of the pipeline.}
	\label{fig:pipeline}
\end{figure}

Thus, our pipeline can be visualized as a funnel (shown in Figure~\ref{fig:pipeline}), where the quantity decreases until it reaches the end product.

From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated. We discuss this possibility, and other concepts such as limitations in the following chapter.

>>>>

\subsection[The Pipeline]{Understanding the pipeline}
This section serves to represent our pipeline quantitatively and graphically. Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

@@

From our research, it is clear that E-Mail Header Injection is quite widespread as a vulnerability, appearing on \successDelta\ of forms that we were able to perform automated attacks on. This value acts as a lower bound for E-Mail Header Injection vulnerability, and can quite easily be much more if the attacks were of a more concentrated nature, crafted for the individual websites and less automated.
